Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-12-31 ms.tex
added another long dark ramp time series, this time w/ NCDHAS applied.
fixed the time series figure after correcting the unsigned int issue in the pairwise subtraction.
more on the dark frame time series.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{long_dark_phot.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations. }\label{fig:longDarkPhot}
\end{figure}

>>>>

It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car asic, and how much they contribute to the error budget.
The dark frames do not contain the photon noise in the background nor the issues with the photometric stability of illumination lamps, which are a persistent challenge with ground-based tests.
We study here the contributions from read noise and dark current.
However, there could be subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where non-illuminated pixels in the images correlate with illuminated ones.

The long dark frames used for detector characterization are 108 groups of 1 frame each read out if full frame mode and are 10.7 sec in duration for one long integration making up one exposure.
These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 2  minus integration 1, 4 minus 3, 6 minus 5 etc.).
Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
In the raw data, there are 4 prominent vertical stripes due to offsets in the read-out amplifiers.
Additionally, there obvious correlations along the fast-read direction (horizontally) due to 1/f noise.

As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.

What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in FIgure \ref{fig:longDarkPhot}.
In this example, reference pixel correction appears to introduce extra noise into a photometric aperture.
However, as an order of magnitude estimate, the total noise in these frames is $\sim$10 DN, compared with the 3$\times 10^{6}$ DN in our CV3 detector stability test.
Therefore, the read noise contributions are expected to be $\sim$ 3 ppm.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_phot.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_phot_red.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top Left:} The time series constructed from raw dark frames.
{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied. 
{\it Bottom Left:} An example read pair subtraction with an overlay of the apertures.
{\it Bottom Right:} AN example read pair subtraction after reduction steps with an overlay of the apertures.}\label{fig:longDarkPhot}
\end{figure*}
